Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Wording
using small letters in section titles.

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Hspec, inspired by
RSpec~\cite{rspec}, allows to document Haskell code with
\emph{properties} and \emph{code examples}, verifies examples and
tests properties, and creates an informal specification document.

@@

\begin{quote}
Hspec can be used to document the behavior of a system in a way that
is similar to a specification.  All facets of the system are described
with examples and properties, including every possible corner case.

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec~\cite{rspec}, supports
both code examples and \emph{properties} as evidence.
It can verify examples and tests properties, and it can create an
informal specification document from that.

@@

\begin{quote}
Hspec can be used to document the behavior of a system in a way that
is similar to a specification.  All facets of the system should be
described with examples and properties, including every possible
corner case.
